### 2020-05-01 final_report/results.tex
incorporate both changesets
Minor changes

Having selected ANNs, GBTs, ERTs, RBFs and SVMs based on the results of
experiments~2-3, we utilised the best-performing hyperparameter
assignments. In pursuit of goal~(a), the best approximator (no.~1,
ANN) achieved~$R^2=\num{0.998}$ and mean prediction
time~$\overline{t}_{\text{pred.}}=\SI{1.124}{\micro\second}$. These correspond
to a standard error of regression~$S=\num{0.013}$ and a relative speedup~$\omega=\num{6916416} \times$
with respect to the MC TBR evaluation baseline measured during run~1
(see~\cref{tbl:sampling-runs} for details). Satisfying
goal~(b), the fastest model (no.~2, ANN) features~$R^2=\num{0.985}$,
$\overline{t}_{\text{pred.}}=\SI{0.898}{\micro\second}$, $S=\num{0.033}$
and~$\omega=\num{8659251} \times$.
While these surrogates
were trained on the entire available set of~\num{500000} datapoints, in our
attempts to satisfy goal~(c) we also trained a more simplified model (no.~4, GBT)
that achieved~$R^2=\num{0.913}$,
$\overline{t}_{\text{pred.}}=\SI{6.125}{\micro\second}$, $S=\num{0.072}$ and $\omega=\num{1269777} \times$
with only a set of size~\num{10000}.

@@

\begin{equation}
	\text{TBR} = \frac{1}{|C|}\sum_{i \in C} \left[ \frac{1 + \sin(2\pi n (x_i - 1/2)) }{2} \right]
\end{equation}

>>>>

Having selected ANNs, GBTs, ERTs, RBFs and SVMs based on the results of
experiments~2-3, we utilised the best-performing hyperparameter
assignments. In pursuit of goal~(a), the best approximator (no.~1,
ANN) achieved~$R^2=\num{0.998}$ and mean prediction
time~$\overline{t}_{\text{pred.}}=\SI{1.124}{\micro\second}$. These correspond
to a standard error of regression~$S=\num{0.013}$ and a relative speedup~$\omega=\num{6916416} \times$
with respect to the MC TBR evaluation baseline measured during run~1
(see~\cref{tbl:sampling-runs} for details). Satisfying
goal~(b), the fastest model (no.~2, ANN) achieves~$R^2=\num{0.985}$,
$\overline{t}_{\text{pred.}}=\SI{0.898}{\micro\second}$, $S=\num{0.033}$
and~$\omega=\num{8659251} \times$.
While these surrogates
were trained on the entire available set of~\num{500000} datapoints, to satisfy goal~(c) we also trained a more simplified model (no.~4, GBT)
that achieved~$R^2=\num{0.913}$,
$\overline{t}_{\text{pred.}}=\SI{6.125}{\micro\second}$, $S=\num{0.072}$ and $\omega=\num{1269777} \times$
with a set of size only~\num{10000}.

@@

\begin{equation}
	\text{TBR} = \frac{1}{|C|}\sum_{i \in C} \left[1 + \sin(2\pi n (x_i - 1/2)) \right]
\end{equation}
